---
title: ""
output:   
  html_document:
    theme: yeti
---

data pulled: 2018-07-10  
date created: 2018-07-20      
date last edited: 2018-07-22        
date ran: `r Sys.Date()`


```{r datacleaning, include=FALSE, warning = FALSE}

#This script does not include participants currently in progress (defined as incomplete 'termination checklist')

library(reshape)
library(tidyverse)
library(ggplot2)
library(plotly)
library(plyr)
library(dplyr)
library('ggpubr')
library('Cairo')

#set options
theme_set(theme_minimal())

#read in csv
df <- read.csv('SPINS_terminal_2018-07-10.csv', header = FALSE)  #contents of file system
demo <- read.csv('SPINS_REDCap_2018-07-12.csv', header = TRUE, na.strings=c("","NA")) #demographics export from REDCap

#cut out all bval, bvec, json, and ppm file extensions
df <- as.data.frame(df[!grepl('.bval', df[[1]]),])
df <- as.data.frame(df[!grepl('.bvec', df[[1]]),])
df <- as.data.frame(df[!grepl('.json', df[[1]]),]) 
df <- as.data.frame(df[!grepl('.ppm', df[[1]]),])

#rename variable
names(df)[1] <- "scan"

#remove path from string
df$scan <- substring(df$scan, 30)

#split path into two columns; one with participant ID
df <- colsplit(df$scan,'/',names=c("subject_id","scan"))

#remove phantoms
df <- as.data.frame(df[- grep('_PHA_', df$scan),]) #ADNI and FBIRN phantoms
df <- as.data.frame(df[!grepl('_P00', df$subject_id),]) #human phantoms
df <- as.data.frame(df[!grepl('999', df$subject_id),]) #test participant
df <- as.data.frame(df[!grepl('998', df$subject_id),]) #test participant

#cut out the scan ID from the file string
df$scan <- substring(df$scan, 22)

#bring out scan name
df$scan_name <- sapply(strsplit(df$scan, '_'), `[`, 1)

#rename DTI
df$scan_name[df$scan_name == "DTI60-1000"] <- "DTI"

#remove scans we don't need to include these in count
df <- as.data.frame(df[!grepl('FMAP-', df$scan_name),]) #don't need fmaps
df <- as.data.frame(df[- grep('^PD$', df$scan_name),]) #don't need whatever is currently called PD - second file?

#remove scan column; no longer needed
df <- subset(df, select= -scan)

#turn from long to wide format
df <- df %>%
  group_by(subject_id, scan_name) %>%
  dplyr::summarise(count = n()) %>%
  ungroup() %>%
  spread(scan_name, count, fill = 0)

#add column for site info
df$scanner <- substring(df$subject_id, 7, 9)

#recalculate all scan counts (get rid of counting extra scans - which may be error - have made issues to follow up)
df$DTI <- ifelse(df$DTI >= 1, 1, df$DTI)
df$EMP <- ifelse(df$EMP >= 3, 3, df$EMP)
df$FLAIR <- ifelse(df$FLAIR >= 1, 1, df$FLAIR)
df$IMI <- ifelse(df$IMI >= 1, 1, df$IMI)
df$OBS <- ifelse(df$OBS >= 1, 1, df$OBS)
df$PDT2 <- ifelse(df$PDT2 >= 1, 1, df$PDT2)
df$RST <- ifelse(df$RST >= 1, 1, df$RST)
df$T2 <- ifelse(df$T2 >= 1, 1, df$T2)
df$T1 <- ifelse(df$T1 >= 1 & (df$scanner == 'CMH' | df$scanner == 'CMP'), 1, df$T1)
df$T1 <- ifelse(df$T1 >= 3 & (df$scanner == 'MRC' | df$scanner == 'MRP'), 3, df$T1)
df$T1 <- ifelse(df$T1 >= 1 & (df$scanner == 'ZHH' | df$scanner == 'ZHP'), 1, df$T1)

#make a site variable
df$site <- NA
df$site <- ifelse(df$scanner == 'CMH' | df$scanner == 'CMP', "Toronto", df$site)
df$site <- ifelse(df$scanner == 'MRC' | df$scanner == 'MRP', "Maryland", df$site)
df$site <- ifelse(df$scanner == 'ZHH' | df$scanner == 'ZHP', "New York", df$site)

#make revised score for T1
df$T1_r <- ifelse(df$site == "Maryland" & df$T1 == 3, 1, 0)
df$T1_r <- ifelse(df$site != "Maryland", df$T1, df$T1_r)

#make revised score for EMP
df$EMP_r <- ifelse(df$EMP == 3, 1, 0)

#make a variable for completeness
df$mri_complete_igFLAIR <- ifelse( #ignoring FLAIR in our 'total' count
    df$DTI == 1 & 
    df$IMI == 1 &
    df$OBS == 1 &
    df$PDT2 == 1 &      
    df$RST == 1 &     
    df$T2 == 1 &
    df$T1_r == 1 &
    df$EMP_r == 1, 1, 0)   

df$mri_complete_inFLAIR <- ifelse( #including FLAIR in our 'total' count
    df$DTI == 1 & 
    df$FLAIR == 1 &
    df$IMI == 1 &
    df$OBS == 1 &
    df$PDT2 == 1 &      
    df$RST == 1 &     
    df$T2 == 1 &
    df$T1_r == 1 &
    df$EMP_r == 1, 1, 0)   

#review data from REDCap
demo <- demo[,c(
  'record_id', 
  'redcap_event_name', #group
  'consent_dt', #date of consent
  'demo_age_study_entry', #age at study entry
  'demo_sex_birth', #sex
  'demo_highest_grade_self', #education
  'subsum_socog_test', #completed scog and ncog
  'term_premature_yn', #premature withdrawal
  'term_no_longer_elg', #no longer meet eligibility
  'term_rdoc')]  #data sharing

#recode variables
demo$redcap_event_name <- ifelse(demo$redcap_event_name == 'case_arm_2', 'case', 'control') #group
demo$demo_sex_birth <- ifelse(demo$demo_sex_birth == 1, 'female', 'male') #sex
demo$subsum_socog_test <- ifelse(demo$subsum_socog_test == 1, 'YES', demo$subsum_socog_test) #scog/ncog
demo$subsum_socog_test <- ifelse(demo$subsum_socog_test == 0, 'NO', demo$subsum_socog_test) #scog/ncog
demo$term_premature_yn <- ifelse(demo$term_premature_yn == 0, 'NO', demo$term_premature_yn) #withdrawn?
demo$term_premature_yn <- ifelse(demo$term_premature_yn == 1, 'YES', demo$term_premature_yn) #withdrawn?
demo$term_no_longer_elg <- ifelse(is.na(demo$term_no_longer_elg), 'NO', 'YES' ) 
demo$term_rdoc <- ifelse(demo$term_rdoc == 0, 'NO', 'YES' ) 

#change variable names
names(demo)[names(demo) == 'redcap_event_name'] <- 'group'
names(demo)[names(demo) == 'demo_age_study_entry'] <- 'age'
names(demo)[names(demo) == 'demo_sex_birth'] <- 'sex'
names(demo)[names(demo) == 'demo_highest_grade_self'] <- 'education'
names(demo)[names(demo) == 'subsum_socog_test'] <- 'cog_complete'
names(demo)[names(demo) == 'term_premature_yn'] <- 'terminate'
names(demo)[names(demo) == 'term_no_longer_elg'] <- 'not_eligible'
names(demo)[names(demo) == 'term_rdoc'] <- 'datashare'

#remove last 2 characters of participant ID from the file system, so can merge
df$subject_id <- substring(df$subject_id, 1, 14)

#merge df and demo dataframes
df <- merge(demo, df, by.x = 'record_id', by.y = 'subject_id', all.x = TRUE) 
rm(demo)

#remove participants that didn't meet eligibility
#df<-df[!(df$not_eligible=='YES'),] #32

#remove participants that didn't consent to data sharing OR shouldn't be shared for another reason
#df<-df[!(df$datashare =='NO'),] #26

#rearrange columns
df <- df[, c(
  "record_id",  
  "group",                
  "site", 
  "scanner",              
  "consent_dt",           
  "age",                  
  "sex",                  
  "education",
  "T1_r", 
  "T2",  
  "PDT2", 
  "DTI",   
  "RST", 
  "IMI",                  
  "OBS",                  
  "EMP_r",                  
  "FLAIR",               
  "mri_complete_igFLAIR", 
  "mri_complete_inFLAIR",
  "cog_complete",        
  "terminate",
  'not_eligible', 
  'datashare'
)]

#name columns
names(df)[names(df) == 'T1_r'] <- 'T1'
names(df)[names(df) == 'EMP_r'] <- 'EA'

#fill in site and scanner info
df$scanner <- substring(df$record_id, 7, 9)
df$site <- ifelse(df$scanner == 'CMH' | df$scanner == 'CMP', "Toronto", df$site)
df$site <- ifelse(df$scanner == 'MRC' | df$scanner == 'MRP', "Maryland", df$site)
df$site <- ifelse(df$scanner == 'ZHH' | df$scanner == 'ZHP', "New York", df$site)

#remove rows if consent date or sex is NA (either didn't complete first assessment, or not yet entered)
df <- df[!is.na(df$consent_dt),]
df <- df[!is.na(df$sex),]

#remove participants currently in progress (ascertained by NA in 'cog_complete' and 'terminate')
df <- df[!is.na(df$cog_complete),]
df <- df[!is.na(df$terminate),]

#write csv
#write.csv(df, 'generated_csvs/SPINS_participantList.csv', row.names=FALSE)

```

```{r imaging_df, include = FALSE, warning = FALSE}

#combine site and scanner information in new variable
df$scanner_sites <- paste(df$site, df$scanner, sep = " ")

#we are going to exclude FLAIR from counts of complete participants - rename variable
names(df)[names(df) == 'mri_complete_igFLAIR'] <- 'TOTAL'

#make dataframe of just imaging data we need
imaging_df <- df[, c(
  "record_id",
  "scanner_sites",
  'group',
  'sex',
  'cog_complete',
  "T1",
  "T2",
  "PDT2",
  "DTI",
  "RST",
  "IMI",
  "OBS",
  "FLAIR",
  "TOTAL")]

#melt data to make easier to work with
  imaging_df <- melt(imaging_df , id.vars = c("record_id", "scanner_sites", 'group', 'sex', 'cog_complete'))

#make sure factor variables are factors
  imaging_df$scanner_sites <- as.factor(imaging_df$scanner_sites)
  imaging_df$group <- as.factor(imaging_df$group)
  imaging_df$sex <- as.factor(imaging_df$sex)
  imaging_df$cog_complete <- as.factor(imaging_df$cog_complete)

#adjust completion levels for value factor
   imaging_df$value <- as.factor(imaging_df$value)
   levels(imaging_df$value) <- c(levels(imaging_df$value), "complete", "incomplete")
   imaging_df$value[imaging_df$value == "1"]  <- "complete"
   imaging_df$value[imaging_df$value == "0"]  <- "incomplete"
   imaging_df$value <- droplevels(imaging_df$value, exclude = c("1", "0"))
   
#set up facet plots labels using labeller
scale_labels = c(
  "T1" = "T1",
  "T2" = "T2",
  "PDT2" = "PDT2",
  "DTI" = "DTI",
  "RST" = "RST",
  "IMI" = "IMI",
  "OBS" = "OBS",
  "FLAIR" = "FLAIR", 
  "TOTAL" = "TOTAL")
   
```

```{r plotting_df_site, include = FALSE, warning = FALSE}

###################
#sites - all (tab 1)
###################

#aggregate data for plots
  imaging_df_site1 <- ddply(imaging_df, .var = c("scanner_sites", "variable"), .fun = summarise,
                  complete = sum(value %in% "complete"),
                  incomplete = sum(value %in% "incomplete"),
                  count_complete = sum(complete),
                  count_total = sum(complete + incomplete))

#melt data for plotting
  imaging_df_site1 <- melt(imaging_df_site1, id.vars = c("scanner_sites", "variable", 'count_complete', 'count_total'))
  names(imaging_df_site1)[2] <- "scan"

#set up fill colours for bargraphs
imaging_df_site1$FillColor <- ordered(paste0(imaging_df_site1$scanner_sites, "_", imaging_df_site1$variable), levels=c(
   "Toronto CMH_incomplete", "Toronto CMH_complete",
   "Toronto CMP_incomplete", "Toronto CMP_complete",
   "Maryland MRC_incomplete", "Maryland MRC_complete",
   "Maryland MRP_incomplete", "Maryland MRP_complete",
   "New York ZHH_incomplete", "New York ZHH_complete",
   "New York ZHP_incomplete", "New York ZHP_complete"))

#set up manual colour scale, with site colours and alpha
colours_site1 = c(
  "Toronto CMH_incomplete" = alpha("#6c2e8a", .25),
  "Toronto CMH_complete" = alpha("#6c2e8a", 1),
  "Toronto CMP_incomplete" = alpha("#6c2e8a", .25),
  "Toronto CMP_complete" = alpha("#6c2e8a", 1),
  
  "Maryland MRC_incomplete" = alpha("#e01e39", .25),
  "Maryland MRC_complete" = alpha("#e01e39", 1),
  "Maryland MRP_incomplete" = alpha("#e01e39", .25),
  "Maryland MRP_complete" = alpha("#e01e39", 1),
  
  "New York ZHH_incomplete" = alpha("#1e4698", .25),
  "New York ZHH_complete" = alpha("#1e4698", 1),
  "New York ZHP_incomplete" = alpha("#1e4698", .25),
  "New York ZHP_complete" = alpha("#1e4698", 1))

imaging_df_site1$scanner_sites <- factor(imaging_df_site1$scanner_sites, levels = c(
  'Toronto CMH', 
  'Toronto CMP',
  'Maryland MRC', 
  'Maryland MRP',
  'New York ZHH', 
  'New York ZHP'))

#make a variable for sites
imaging_df_site1$site <- str_sub(imaging_df_site1$scanner_sites,-3,-1)


###################
#sites - complete only (tab 2)
###################

#aggregate data for plots
  imaging_df_site2 <- ddply(imaging_df, .var = c("scanner_sites", "variable", "cog_complete"), .fun = summarise,
                  complete = sum(value %in% "complete"),
                  incomplete = sum(value %in% "incomplete"),
                  count_complete = sum(complete),
                  count_total = sum(complete + incomplete))

#remove rows for incomplete cognition
imaging_df_site2 <- imaging_df_site2[(imaging_df_site2$cog_complete=='YES'), ]

#remove cog_complete column
imaging_df_site2 <- subset(imaging_df_site2, select = -cog_complete)

#melt data for plotting
  imaging_df_site2 <- melt(imaging_df_site2, id.vars = c("scanner_sites", "variable", 'count_complete', 'count_total'))
  names(imaging_df_site2)[2] <- "scan"

#set up fill colours for bargraphs
imaging_df_site2$FillColor <- ordered(paste0(imaging_df_site2$scanner_sites, "_", imaging_df_site2$variable), levels=c(
   "Toronto CMH_incomplete", "Toronto CMH_complete",
   "Toronto CMP_incomplete", "Toronto CMP_complete",
   "Maryland MRC_incomplete", "Maryland MRC_complete",
   "Maryland MRP_incomplete", "Maryland MRP_complete",
   "New York ZHH_incomplete", "New York ZHH_complete",
   "New York ZHP_incomplete", "New York ZHP_complete"))

#set up manual colour scale, with site colours and alpha
colours_site2 = c(
  "Toronto CMH_incomplete" = alpha("#6c2e8a", .25),
  "Toronto CMH_complete" = alpha("#6c2e8a", 1),
  "Toronto CMP_incomplete" = alpha("#6c2e8a", .25),
  "Toronto CMP_complete" = alpha("#6c2e8a", 1),
  
  "Maryland MRC_incomplete" = alpha("#e01e39", .25),
  "Maryland MRC_complete" = alpha("#e01e39", 1),
  "Maryland MRP_incomplete" = alpha("#e01e39", .25),
  "Maryland MRP_complete" = alpha("#e01e39", 1),
  
  "New York ZHH_incomplete" = alpha("#1e4698", .25),
  "New York ZHH_complete" = alpha("#1e4698", 1),
  "New York ZHP_incomplete" = alpha("#1e4698", .25),
  "New York ZHP_complete" = alpha("#1e4698", 1))

imaging_df_site2$scanner_sites <- factor(imaging_df_site2$scanner_sites, levels = c(
  'Toronto CMH', 
  'Toronto CMP',
  'Maryland MRC', 
  'Maryland MRP',
  'New York ZHH', 
  'New York ZHP'))

#make a variable for sites
imaging_df_site2$site <- str_sub(imaging_df_site2$scanner_sites,-3,-1)
   
```

```{r plotting_df_dx, include = FALSE, warning = FALSE}

###################
#dx - all (tab 3)
###################

#remove incomplete scans
imaging_df_dx1 <- imaging_df[(imaging_df$value=='complete'), ]

#remove sex column
imaging_df_dx1 <- subset(imaging_df_dx1, select = -sex)

#remove cog_complete column - we want even if not complete
imaging_df_dx1 <- subset(imaging_df_dx1, select = -cog_complete)

#aggregate data for plots
imaging_df_dx1 <- ddply(imaging_df_dx1, .var = c("scanner_sites", "variable", 'group'), .fun = summarise,
                  complete = sum(value %in% "complete"))

#change variable name for consistency
names(imaging_df_dx1)[2] <- "scan"

#make a variable for sites
imaging_df_dx1$site <- str_sub(imaging_df_dx1$scanner_sites,-3,-1)

#set up fill colours for bargraphs
imaging_df_dx1$FillColor <- ordered(paste0(imaging_df_dx1$scanner_sites, "_", imaging_df_dx1$group), levels=c(
   "Toronto CMH_case", "Toronto CMH_control",
   "Toronto CMP_case", "Toronto CMP_control",
   "Maryland MRC_case", "Maryland MRC_control",
   "Maryland MRP_case", "Maryland MRP_control",
   "New York ZHH_case", "New York ZHH_control",
   "New York ZHP_case", "New York ZHP_control"))

#set up manual colour scale, with site colours and alpha
colours_dx = c(
  "Toronto CMH_case" = "#d8b70a",
  "Toronto CMH_control" = "#db8c36",
  "Toronto CMP_case" = "#d8b70a",
  "Toronto CMP_control" = "#db8c36",
  
  "Maryland MRC_case" = "#d8b70a",
  "Maryland MRC_control" = "#db8c36",
  "Maryland MRP_case" = "#d8b70a",
  "Maryland MRP_control" = "#db8c36",
  
  "New York ZHH_case" = "#d8b70a",
  "New York ZHH_control" = "#db8c36",
  "New York ZHP_case" = "#d8b70a",
  "New York ZHP_control" = "#db8c36")

###################
#dx - complete only (tab 4)
###################

#remove incomplete scans
imaging_df_dx2 <- imaging_df[(imaging_df$value=='complete'), ]

#remove sex column
imaging_df_dx2 <- subset(imaging_df_dx2, select = -sex)

#remove all participants if incomplete cog data
imaging_df_dx2 <- imaging_df_dx2[(imaging_df_dx2$cog_complete == 'YES'),]

#remove cog_complete column - no longer necessary
imaging_df_dx2 <- subset(imaging_df_dx2, select = -cog_complete)

#aggregate data for plots
imaging_df_dx2 <- ddply(imaging_df_dx2, .var = c("scanner_sites", "variable", 'group'), .fun = summarise,
                  complete = sum(value %in% "complete"))

#change variable name for consistency
names(imaging_df_dx2)[2] <- "scan"

#make a variable for sites
imaging_df_dx2$site <- str_sub(imaging_df_dx2$scanner_sites,-3,-1)

#set up fill colours for bargraphs
imaging_df_dx2$FillColor <- ordered(paste0(imaging_df_dx2$scanner_sites, "_", imaging_df_dx2$group), levels=c(
   "Toronto CMH_case", "Toronto CMH_control",
   "Toronto CMP_case", "Toronto CMP_control",
   "Maryland MRC_case", "Maryland MRC_control",
   "Maryland MRP_case", "Maryland MRP_control",
   "New York ZHH_case", "New York ZHH_control",
   "New York ZHP_case", "New York ZHP_control"))

```

```{r plotting_df_sex, include = FALSE, warning = FALSE}

###################
#sex - all (tab 5)
###################

#remove incomplete scans
imaging_df_sex1 <- imaging_df[(imaging_df$value=='complete'), ]

#remove dx column
imaging_df_sex1 <- subset(imaging_df_sex1, select = -group)

#remove cog_complete column - we want even if not complete
imaging_df_sex1 <- subset(imaging_df_sex1, select = -cog_complete)

#aggregate data for plots
imaging_df_sex1 <- ddply(imaging_df_sex1, .var = c("scanner_sites", "variable", 'sex'), .fun = summarise,
                  complete = sum(value %in% "complete"))

#change variable name for consistency
names(imaging_df_sex1)[2] <- "scan"

#make a variable for sites
imaging_df_sex1$site <- str_sub(imaging_df_sex1$scanner_sites,-3,-1)

#set up fill colours for bargraphs
imaging_df_sex1$FillColor <- ordered(paste0(imaging_df_sex1$scanner_sites, "_", imaging_df_sex1$sex), levels=c(
   "Toronto CMH_female", "Toronto CMH_male",
   "Toronto CMP_female", "Toronto CMP_male",
   "Maryland MRC_female", "Maryland MRC_male",
   "Maryland MRP_female", "Maryland MRP_male",
   "New York ZHH_female", "New York ZHH_male",
   "New York ZHP_female", "New York ZHP_male"))

#set up manual colour scale, with site colours and alpha
colours_sex = c(
  "Toronto CMH_female" = "#ccc591",
  "Toronto CMH_male" = "#b3ccba",
  "Toronto CMP_female" = "#ccc591",
  "Toronto CMP_male" = "#b3ccba",
  
  "Maryland MRC_female" = "#ccc591",
  "Maryland MRC_male" = "#b3ccba",
  "Maryland MRP_female" = "#ccc591",
  "Maryland MRP_male" = "#b3ccba",
  
  "New York ZHH_female" = "#ccc591",
  "New York ZHH_male" = "#b3ccba",
  "New York ZHP_female" = "#ccc591",
  "New York ZHP_male" = "#b3ccba")

###################
#sex - complete only (tab 6)
###################

#remove incomplete scans
imaging_df_sex2 <- imaging_df[(imaging_df$value=='complete'), ]

#remove diagnosis column
imaging_df_sex2 <- subset(imaging_df_sex2, select = -group)

#remove all participants if incomplete cog data
imaging_df_sex2 <- imaging_df_sex2[(imaging_df_sex2$cog_complete == 'YES'),]

#remove cog_complete column - no longer necessary
imaging_df_sex2 <- subset(imaging_df_sex2, select = -cog_complete)

#aggregate data for plots
imaging_df_sex2 <- ddply(imaging_df_sex2, .var = c("scanner_sites", "variable", 'sex'), .fun = summarise,
                  complete = sum(value %in% "complete"))

#change variable name for consistency
names(imaging_df_sex2)[2] <- "scan"

#make a variable for sites
imaging_df_sex2$site <- str_sub(imaging_df_sex2$scanner_sites,-3,-1)

#set up fill colours for bargraphs
imaging_df_sex2$FillColor <- ordered(paste0(imaging_df_sex2$scanner_sites, "_", imaging_df_sex2$sex), levels=c(
   "Toronto CMH_female", "Toronto CMH_male",
   "Toronto CMP_female", "Toronto CMP_male",
   "Maryland MRC_female", "Maryland MRC_male",
   "Maryland MRP_female", "Maryland MRP_male",
   "New York ZHH_female", "New York ZHH_male",
   "New York ZHP_female", "New York ZHP_male"))

```


#SPINS: Counts of usable imaging data {.tabset}
<br>

These 6 tabbed plots show the counts of usable imaging data by acquisition type, where 'usable' includes data that passed QC from participants who continued to meet eligibility criteria throughout the study, and did not revoke consent to data sharing. Note that the ‘TOTAL’ facet does not include FLAIR scans in its count. 

<br>
<br>


##MRI x site

```{r plot_imaging_tab1, echo = FALSE, warning = FALSE, message = FALSE, fig.width= 15, fig.height= 9.5}

#plot
plot1 <- ggplot(imaging_df_site1, aes(x = scanner_sites)) +
  facet_wrap(~scan, nrow = 1, labeller = as_labeller(scale_labels)) +
  geom_bar(color = 'black', aes(weight = value, fill = FillColor)) +
  geom_text(aes(x = scanner_sites, y= count_total, label=count_complete), vjust = -.5, size = 5) +
  scale_fill_manual(
    breaks=c("Toronto CMH_complete","Maryland MRC_complete", "New York ZHH_complete"),
    labels=c('Toronto', 'Maryland', 'New York'),
    values = colours_site1) +
  scale_x_discrete(breaks=c('Toronto CMH', 'Toronto CMP', 'Maryland MRC', 'Maryland MRP', 'New York ZHH', 'New York ZHP'),
        labels=c('CMH', 'CMP', 'MRC', 'MRP', 'ZHH', 'ZHP')) +
  ylab("total count scanned") +
  xlab("") +
  ylim(-3,150) +
  theme(axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 90, hjust = 1),
    text = element_text(size=16),
    legend.position='top',
    legend.title=element_blank(),
    panel.background = element_rect(fill = '#f5f5f5'),
    panel.grid.major.x = element_blank() ,
    panel.grid.major.y = element_line(size=.5, color="white"),
    panel.grid.minor.x = element_blank() ,
    panel.grid.minor.y = element_line(size=.5, color="white"))

plot1

```

> __Summary:__ We have `r sum(imaging_df_site1[imaging_df_site1$scan == 'TOTAL' & imaging_df_site1$variable == 'complete', 'count_complete'], na.rm = TRUE)` participants with complete imaging data (Toronto = `r sum(imaging_df_site1[imaging_df_site1$site %in% c('CMH', 'CMP') & imaging_df_site1$scan == 'TOTAL' & imaging_df_site1$variable == 'complete', 'count_complete'], na.rm = TRUE)`, Maryland = `r sum(imaging_df_site1[imaging_df_site1$site %in% c('MRC', 'MRP') & imaging_df_site1$scan == 'TOTAL' & imaging_df_site1$variable == 'complete', 'count_complete'], na.rm = TRUE)`, New York = `r sum(imaging_df_site1[imaging_df_site1$site %in% c('ZHH', 'ZHP') & imaging_df_site1$scan == 'TOTAL' & imaging_df_site1$variable == 'complete', 'count_complete'], na.rm = TRUE)`; including `r sum(imaging_df_site1[imaging_df_site1$site %in% c('CMP', 'MRP', 'ZHP') & imaging_df_site1$scan == 'TOTAL' & imaging_df_site1$variable == 'complete', 'count_complete'], na.rm = TRUE)` total on PRISMA).
<br>

__Note:__ Solid colours show complete scans. The value at the top of each bar indicates how many participants completed the given scan. Semi-transparency shows how many participants did not complete a given acquisition, for participants that completed at least one acquisition). 

##MRI ~ cog x site

```{r imaging_tab2, echo = FALSE, warning = FALSE, message = FALSE, fig.width= 15, fig.height= 9.5}

#plot
plot2 <- ggplot(imaging_df_site2, aes(x = scanner_sites)) +
  facet_wrap(~scan, nrow = 1, labeller = as_labeller(scale_labels)) +
  geom_bar(color = 'black', aes(weight = value, fill = FillColor)) +
  geom_text(aes(x = scanner_sites, y= count_total, label=count_complete), vjust = -.5, size = 5) +
  scale_fill_manual(
    breaks=c("Toronto CMH_complete","Maryland MRC_complete", "New York ZHH_complete"),
    labels=c('Toronto', 'Maryland', 'New York'),
    values = colours_site2) +
  scale_x_discrete(breaks=c('Toronto CMH', 'Toronto CMP', 'Maryland MRC', 'Maryland MRP', 'New York ZHH', 'New York ZHP'),
        labels=c('CMH', 'CMP', 'MRC', 'MRP', 'ZHH', 'ZHP')) +
  ylab("total count scanned") +
  xlab("") +
  ylim(-3,150) +
  theme(axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 90, hjust = 1),
    text = element_text(size=16),
    legend.position='top',
    legend.title=element_blank(),
    panel.background = element_rect(fill = '#f5f5f5'),
    panel.grid.major.x = element_blank() ,
    panel.grid.major.y = element_line(size=.5, color="white"),
    panel.grid.minor.x = element_blank() ,
    panel.grid.minor.y = element_line(size=.5, color="white"))

plot2

```

> __Summary:__ We have `r sum(imaging_df_site2[imaging_df_site2$scan == 'TOTAL' & imaging_df_site2$variable == 'complete', 'count_complete'], na.rm = TRUE)` participants with complete imaging and cognitive data (Toronto = `r sum(imaging_df_site2[imaging_df_site2$site %in% c('CMH', 'CMP') & imaging_df_site2$scan == 'TOTAL' & imaging_df_site2$variable == 'complete', 'count_complete'], na.rm = TRUE)`, Maryland = `r sum(imaging_df_site2[imaging_df_site2$site %in% c('MRC', 'MRP') & imaging_df_site2$scan == 'TOTAL' & imaging_df_site2$variable == 'complete', 'count_complete'], na.rm = TRUE)`, New York = `r sum(imaging_df_site2[imaging_df_site2$site %in% c('ZHH', 'ZHP') & imaging_df_site2$scan == 'TOTAL' & imaging_df_site2$variable == 'complete', 'count_complete'], na.rm = TRUE)`; including `r sum(imaging_df_site2[imaging_df_site2$site %in% c('CMP', 'MRP', 'ZHP') & imaging_df_site2$scan == 'TOTAL' & imaging_df_site2$variable == 'complete', 'count_complete'], na.rm = TRUE)` total on PRISMA).
<br>

__Note:__ Solid colours show complete scans. The value at the top of each bar indicates how many participants completed the given scan. Semi-transparency shows how many participants did not complete a given acquisition, for participants that completed at least one acquisition). 


##MRI x dx

```{r imaging_dx_tab3, echo = FALSE, warning = FALSE, message = FALSE, fig.width= 15, fig.height= 9.5}

#plot
plot3 <- ggplot(imaging_df_dx1, aes(x = scanner_sites)) +
  facet_wrap(~scan, nrow = 1, labeller = as_labeller(scale_labels)) +
  geom_bar(color = 'black', aes(weight = complete, fill= FillColor)) + 
  geom_text(color = 'black', aes(y = complete, fill= FillColor, label = complete), position = position_stack(), vjust = 1.5, size = 5) +
  scale_x_discrete(breaks=c('Toronto CMH', 'Toronto CMP', 'Maryland MRC', 'Maryland MRP', 'New York ZHH', 'New York ZHP'),
        labels=c('CMH', 'CMP', 'MRC', 'MRP', 'ZHH', 'ZHP'),
        limits=c('Toronto CMH', 'Toronto CMP', 'Maryland MRC', 'Maryland MRP', 'New York ZHH', 'New York ZHP')) +
  scale_fill_manual(
    breaks=c("Toronto CMH_case","Toronto CMH_control"),
    labels=c('SSD', 'HC'),
    values = colours_dx) +
  ylab("total count scanned") +
  xlab("") +
  ylim(-3,150) +
  theme(axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 90, hjust = 1),
    text = element_text(size=16),
    legend.position='top',
    legend.title=element_blank(),
    panel.background = element_rect(fill = '#f5f5f5'),
    panel.grid.major.x = element_blank() ,
    panel.grid.major.y = element_line(size=.5, color="white"),
    panel.grid.minor.x = element_blank() ,
    panel.grid.minor.y = element_line(size=.5, color="white"))

plot3

```

> __Summary:__ We have `r sum(imaging_df_dx1[imaging_df_dx1$scan == 'TOTAL' & imaging_df_dx1$group== 'case', 'complete'], na.rm = TRUE)` SSD participants (Toronto = `r sum(imaging_df_dx1[imaging_df_dx1$site %in% c('CMH', 'CMP') & imaging_df_dx1$scan == 'TOTAL' & imaging_df_dx1$group== 'case', 'complete'], na.rm = TRUE)`, Maryland = `r sum(imaging_df_dx1[imaging_df_dx1$site %in% c('MRC', 'MRP') & imaging_df_dx1$scan == 'TOTAL' & imaging_df_dx1$group== 'case', 'complete'], na.rm = TRUE)`, New York = `r sum(imaging_df_dx1[imaging_df_dx1$site %in% c('ZHH', 'ZHP') & imaging_df_dx1$scan == 'TOTAL' & imaging_df_dx1$group== 'case', 'complete'], na.rm = TRUE)`; including `r sum(imaging_df_dx1[imaging_df_dx1$site %in% c('CMP', 'MRP', 'ZHP') & imaging_df_dx1$scan == 'TOTAL' & imaging_df_dx1$group== 'case', 'complete'], na.rm = TRUE)` total on PRISMA), and `r sum(imaging_df_dx1[imaging_df_dx1$scan == 'TOTAL' & imaging_df_dx1$group== 'control', 'complete'], na.rm = TRUE)` HC participants (Toronto = `r sum(imaging_df_dx1[imaging_df_dx1$site %in% c('CMH', 'CMP') & imaging_df_dx1$scan == 'TOTAL' & imaging_df_dx1$group== 'control', 'complete'], na.rm = TRUE)`, Maryland = `r sum(imaging_df_dx1[imaging_df_dx1$site %in% c('MRC', 'MRP') & imaging_df_dx1$scan == 'TOTAL' & imaging_df_dx1$group== 'control', 'complete'], na.rm = TRUE)`, New York = `r sum(imaging_df_dx1[imaging_df_dx1$site %in% c('ZHH', 'ZHP') & imaging_df_dx1$scan == 'TOTAL' & imaging_df_dx1$group== 'control', 'complete'], na.rm = TRUE)`; including `r sum(imaging_df_dx1[imaging_df_dx1$site %in% c('CMP', 'MRP', 'ZHP') & imaging_df_dx1$scan == 'TOTAL' & imaging_df_dx1$group== 'control', 'complete'], na.rm = TRUE)` total on PRISMA) with complete imaging data. 

## MRI ~ cog x dx

```{r imaging_dx_tab4, echo = FALSE, warning = FALSE, message = FALSE, fig.width= 15, fig.height= 9.5}

#plot
plot4 <- ggplot(imaging_df_dx2, aes(x = scanner_sites)) +
  facet_wrap(~scan, nrow = 1, labeller = as_labeller(scale_labels)) +
  geom_bar(color = 'black', aes(weight = complete, fill= FillColor)) +
  geom_text(color = 'black', aes(y = complete, fill= FillColor, label = complete), position = position_stack(), vjust = 1.5, size = 5) +
  scale_x_discrete(breaks=c('Toronto CMH', 'Toronto CMP', 'Maryland MRC', 'Maryland MRP', 'New York ZHH', 'New York ZHP'),
        labels=c('CMH', 'CMP', 'MRC', 'MRP', 'ZHH', 'ZHP'),
        limits=c('Toronto CMH', 'Toronto CMP', 'Maryland MRC', 'Maryland MRP', 'New York ZHH', 'New York ZHP')) +
  scale_fill_manual(
    breaks=c("Toronto CMH_case","Toronto CMH_control"),
    labels=c('SSD', 'HC'),
    values = colours_dx) +
  ylab("total count scanned") +
  xlab("") +
  ylim(-3,150) +
  theme(axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 90, hjust = 1),
    text = element_text(size=16),
    legend.position='top',
    legend.title=element_blank(),
    panel.background = element_rect(fill = '#f5f5f5'),
    panel.grid.major.x = element_blank() ,
    panel.grid.major.y = element_line(size=.5, color="white"),
    panel.grid.minor.x = element_blank() ,
    panel.grid.minor.y = element_line(size=.5, color="white"))

plot4

```

> __Summary:__ We have `r sum(imaging_df_dx2[imaging_df_dx2$scan == 'TOTAL' & imaging_df_dx2$group== 'case', 'complete'], na.rm = TRUE)` SSD participants (Toronto = `r sum(imaging_df_dx2[imaging_df_dx2$site %in% c('CMH', 'CMP') & imaging_df_dx2$scan == 'TOTAL' & imaging_df_dx2$group== 'case', 'complete'], na.rm = TRUE)`, Maryland = `r sum(imaging_df_dx2[imaging_df_dx2$site %in% c('MRC', 'MRP') & imaging_df_dx2$scan == 'TOTAL' & imaging_df_dx2$group== 'case', 'complete'], na.rm = TRUE)`, New York = `r sum(imaging_df_dx2[imaging_df_dx2$site %in% c('ZHH', 'ZHP') & imaging_df_dx2$scan == 'TOTAL' & imaging_df_dx2$group== 'case', 'complete'], na.rm = TRUE)`; including `r sum(imaging_df_dx2[imaging_df_dx2$site %in% c('CMP', 'MRP', 'ZHP') & imaging_df_dx2$scan == 'TOTAL' & imaging_df_dx2$group== 'case', 'complete'], na.rm = TRUE)` total on PRISMA), and `r sum(imaging_df_dx2[imaging_df_dx2$scan == 'TOTAL' & imaging_df_dx2$group== 'control', 'complete'], na.rm = TRUE)` HC participants (Toronto = `r sum(imaging_df_dx2[imaging_df_dx2$site %in% c('CMH', 'CMP') & imaging_df_dx2$scan == 'TOTAL' & imaging_df_dx2$group== 'control', 'complete'], na.rm = TRUE)`, Maryland = `r sum(imaging_df_dx2[imaging_df_dx2$site %in% c('MRC', 'MRP') & imaging_df_dx2$scan == 'TOTAL' & imaging_df_dx2$group== 'control', 'complete'], na.rm = TRUE)`, New York = `r sum(imaging_df_dx2[imaging_df_dx2$site %in% c('ZHH', 'ZHP') & imaging_df_dx2$scan == 'TOTAL' & imaging_df_dx2$group== 'control', 'complete'], na.rm = TRUE)`; including `r sum(imaging_df_dx2[imaging_df_dx2$site %in% c('CMP', 'MRP', 'ZHP') & imaging_df_dx2$scan == 'TOTAL' & imaging_df_dx2$group== 'control', 'complete'], na.rm = TRUE)` total on PRISMA) with complete imaging and cognitive data. 

##MRI x sex

```{r imaging_sex_tab5, echo = FALSE, warning = FALSE, message = FALSE, fig.width= 15, fig.height= 9.5}

#plot
plot5 <- ggplot(imaging_df_sex1, aes(x = scanner_sites)) +
  facet_wrap(~scan, nrow = 1, labeller = as_labeller(scale_labels)) +
  geom_bar(color = 'black', aes(weight = complete, fill= FillColor)) +
  geom_text(color = 'black', aes(y = complete, fill= FillColor, label = complete), position = position_stack(), vjust = 1.5, size = 5) +
  scale_x_discrete(breaks=c('Toronto CMH', 'Toronto CMP', 'Maryland MRC', 'Maryland MRP', 'New York ZHH', 'New York ZHP'),
        labels=c('CMH', 'CMP', 'MRC', 'MRP', 'ZHH', 'ZHP'),
        limits=c('Toronto CMH', 'Toronto CMP', 'Maryland MRC', 'Maryland MRP', 'New York ZHH', 'New York ZHP')) +
  scale_fill_manual(
    breaks=c("Toronto CMH_female","Toronto CMH_male"),
    labels=c('female', 'male'),
    values = colours_sex) +
  ylab("total count scanned") +
  xlab("") +
  ylim(-3,150) +
  theme(axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 90, hjust = 1),
    text = element_text(size=16),
    legend.position='top',
    legend.title=element_blank(),
    panel.background = element_rect(fill = '#f5f5f5'),
    panel.grid.major.x = element_blank() ,
    panel.grid.major.y = element_line(size=.5, color="white"),
    panel.grid.minor.x = element_blank() ,
    panel.grid.minor.y = element_line(size=.5, color="white"))

plot5

```

> __Summary:__ We have `r sum(imaging_df_sex1[imaging_df_sex1$scan == 'TOTAL' & imaging_df_sex1$sex== 'female', 'complete'], na.rm = TRUE)` female participants (Toronto = `r sum(imaging_df_sex1[imaging_df_sex1$site %in% c('CMH', 'CMP') & imaging_df_sex1$scan == 'TOTAL' & imaging_df_sex1$sex== 'female', 'complete'], na.rm = TRUE)`, Maryland = `r sum(imaging_df_sex1[imaging_df_sex1$site %in% c('MRC', 'MRP') & imaging_df_sex1$scan == 'TOTAL' & imaging_df_sex1$sex== 'female', 'complete'], na.rm = TRUE)`, New York = `r sum(imaging_df_sex1[imaging_df_sex1$site %in% c('ZHH', 'ZHP') & imaging_df_sex1$scan == 'TOTAL' & imaging_df_sex1$sex== 'female', 'complete'], na.rm = TRUE)`; including `r sum(imaging_df_sex1[imaging_df_sex1$site %in% c('CMP', 'MRP', 'ZHP') & imaging_df_sex1$scan == 'TOTAL' & imaging_df_sex1$sex== 'female', 'complete'], na.rm = TRUE)` total on PRISMA), and `r sum(imaging_df_sex1[imaging_df_sex1$scan == 'TOTAL' & imaging_df_sex1$sex== 'male', 'complete'], na.rm = TRUE)` male participants (Toronto = `r sum(imaging_df_sex1[imaging_df_sex1$site %in% c('CMH', 'CMP') & imaging_df_sex1$scan == 'TOTAL' & imaging_df_sex1$sex== 'male', 'complete'], na.rm = TRUE)`, Maryland = `r sum(imaging_df_sex1[imaging_df_sex1$site %in% c('MRC', 'MRP') & imaging_df_sex1$scan == 'TOTAL' & imaging_df_sex1$sex== 'male', 'complete'], na.rm = TRUE)`, New York = `r sum(imaging_df_sex1[imaging_df_sex1$site %in% c('ZHH', 'ZHP') & imaging_df_sex1$scan == 'TOTAL' & imaging_df_sex1$sex== 'male', 'complete'], na.rm = TRUE)`; including `r sum(imaging_df_sex1[imaging_df_sex1$site %in% c('CMP', 'MRP', 'ZHP') & imaging_df_sex1$scan == 'TOTAL' & imaging_df_sex1$sex== 'male', 'complete'], na.rm = TRUE)` total on PRISMA) with complete imaging data. 

##MRI ~ cog x sex

```{r imaging_sex_tab6, echo = FALSE, warning = FALSE, message = FALSE, fig.width= 15, fig.height= 9.5}

#plot
plot6 <- ggplot(imaging_df_sex2, aes(x = scanner_sites)) +
  facet_wrap(~scan, nrow = 1, labeller = as_labeller(scale_labels)) +
  geom_bar(color = 'black', aes(weight = complete, fill= FillColor)) +
  geom_text(color = 'black', aes(y = complete, fill= FillColor, label = complete), position = position_stack(), vjust = 1.5, size = 5) +
  scale_x_discrete(breaks=c('Toronto CMH', 'Toronto CMP', 'Maryland MRC', 'Maryland MRP', 'New York ZHH', 'New York ZHP'),
        labels=c('CMH', 'CMP', 'MRC', 'MRP', 'ZHH', 'ZHP'),
        limits=c('Toronto CMH', 'Toronto CMP', 'Maryland MRC', 'Maryland MRP', 'New York ZHH', 'New York ZHP')) +
  scale_fill_manual(
    breaks=c("Toronto CMH_female","Toronto CMH_male"),
    labels=c('female', 'male'),
    values = colours_sex) +
  ylab("total count scanned") +
  xlab("") +
  ylim(-3,150) +
  theme(axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 90, hjust = 1),
    text = element_text(size=16),
    legend.position='top',
    legend.title=element_blank(),
    panel.background = element_rect(fill = '#f5f5f5'),
    panel.grid.major.x = element_blank() ,
    panel.grid.major.y = element_line(size=.5, color="white"),
    panel.grid.minor.x = element_blank() ,
    panel.grid.minor.y = element_line(size=.5, color="white"))

plot6

```

> __Summary:__ We have `r sum(imaging_df_sex2[imaging_df_sex2$scan == 'TOTAL' & imaging_df_sex2$sex== 'female', 'complete'], na.rm = TRUE)` female participants (Toronto = `r sum(imaging_df_sex2[imaging_df_sex2$site %in% c('CMH', 'CMP') & imaging_df_sex2$scan == 'TOTAL' & imaging_df_sex2$sex== 'female', 'complete'], na.rm = TRUE)`, Maryland = `r sum(imaging_df_sex2[imaging_df_sex2$site %in% c('MRC', 'MRP') & imaging_df_sex2$scan == 'TOTAL' & imaging_df_sex2$sex== 'female', 'complete'], na.rm = TRUE)`, New York = `r sum(imaging_df_sex2[imaging_df_sex2$site %in% c('ZHH', 'ZHP') & imaging_df_sex2$scan == 'TOTAL' & imaging_df_sex2$sex== 'female', 'complete'], na.rm = TRUE)`; including `r sum(imaging_df_sex2[imaging_df_sex2$site %in% c('CMP', 'MRP', 'ZHP') & imaging_df_sex2$scan == 'TOTAL' & imaging_df_sex2$sex== 'female', 'complete'], na.rm = TRUE)` total on PRISMA), and `r sum(imaging_df_sex2[imaging_df_sex2$scan == 'TOTAL' & imaging_df_sex2$sex== 'male', 'complete'], na.rm = TRUE)` male participants (Toronto = `r sum(imaging_df_sex2[imaging_df_sex2$site %in% c('CMH', 'CMP') & imaging_df_sex2$scan == 'TOTAL' & imaging_df_sex2$sex== 'male', 'complete'], na.rm = TRUE)`, Maryland = `r sum(imaging_df_sex2[imaging_df_sex2$site %in% c('MRC', 'MRP') & imaging_df_sex2$scan == 'TOTAL' & imaging_df_sex2$sex== 'male', 'complete'], na.rm = TRUE)`, New York = `r sum(imaging_df_sex2[imaging_df_sex2$site %in% c('ZHH', 'ZHP') & imaging_df_sex2$scan == 'TOTAL' & imaging_df_sex2$sex== 'male', 'complete'], na.rm = TRUE)`; including `r sum(imaging_df_sex2[imaging_df_sex2$site %in% c('CMP', 'MRP', 'ZHP') & imaging_df_sex2$scan == 'TOTAL' & imaging_df_sex2$sex== 'male', 'complete'], na.rm = TRUE)` total on PRISMA) with complete imaging and cognitive data. 